Reproducible Summary Tables with the gtsummary Package

### 2020-12-11 RJtemplate_gtsummary_submission.tex
Updates from Overleaf

\section{Inline Reporting}\label{in-line-reporting}

@@

\section{Merging and Stacking}\label{merging-and-stacking}

\section{Themes}\label{themes}

@@

many more advanced or fine-grained customizations. Theme elements fall into two categories: (1) elements that modify internal behavior of the functions that is not directly controllable by function arguments, (2) elements that set function argument defaults. The values of these theme elements must align with the functions’ accepted input for the argument.

While a full glossary of customizable theme elements is available via the package documentation (http://www.danieldsjoberg.com/gtsummary/articles/themes.html)
\section{Print Engines}\label{print-engines}

>>>>

\section{Inline Reporting}

@@

\section{Merging and Stacking}

\section{Themes}

@@

For example, using the theme for New England Journal of Medicine, large p-values are rounded to two decimal places and confidence intervals are shown as \texttt{"lb to ub"} instead of \texttt{"lb, ub"}.

\begin{example}
theme_gtsummary_journal("nejm")

glm(response ~ age + grade, trial, family = binomial) %>%
  tbl_regression(exponentiate = TRUE)
\end{example}

\begin{figure}[h!]
  \includegraphics[height=4cm]{nejm.png}
  \centering
\end{figure}

The themes are an evolving feature and we welcome additions of new journals and other useful themes.
A full glossary of customizable theme elements is available in the package documentation (\url{http://www.danieldsjoberg.com/gtsummary/articles/themes.html}).

\section{Print Engines}
